quollr: An R Package for Visualizing 2-D Models from Nonlinear Dimension Reductions in High-Dimensional Space

### 2025-12-17 paper-quollr.Rmd
Updated application cluster color

trimesh_limb <- ggplot() + 
  geom_point(
    data = tsne_limb_scaled_with_cluster,
    aes(
      x = emb1,
      y = emb2,
      color = cluster
    ),
    alpha = 0.3
  ) +
  geom_segment(data = trimesh_data_limb, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#000000",
               linewidth = 1) +
  scale_color_manual(values = c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854','#ffd92f','#e5c494')) +
  interior_annotation("a1", cex = 2) +
  theme(
    aspect.ratio = 1
  )
```

@@

cluster_colors <- c(
    "0" = '#66c2a5', "1" = '#fc8d62', "2" = '#8da0cb',
    "3" = '#e78ac3', "4" = '#a6d854', "5" = '#ffd92f', "6" = '#e5c494'
)

@@

@@

langevitour_output <- langevitour::langevitour(point_data[1:num_highd_col],
                                               lineFrom = edge_data$from_reindexed,
                                               lineTo = edge_data$to_reindexed,
                                               group = factor(point_data$type,
                                                              c("0", "1", "2", "3", "4", "5", "6", "model")),
                                               pointSize = append(rep(point_sizes[1], NROW(df_b)),
                                                                  rep(point_sizes[2], NROW(df))),
                                               levelColors = c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854','#ffd92f','#e5c494', "#000000"),
                                               link=shared_df,
                                               linkFilter=FALSE,
                                               width = "370px", height = "370px")

@@

limb_proj_tsne_model1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2), # size, alpha, color
  line_param = c(0.5, 0.3, "#000000"),
  plot_limits = c(-1.3, 1.4), 
  axis_text_size = 4,
  is_category = TRUE) +
  interior_annotation(label = "a2", cex = 2) + 
  scale_color_manual(values = c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854','#ffd92f','#e5c494'))

@@

limb_proj_tsne_model2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2), # size, alpha, color
  line_param = c(0.5, 0.3, "#000000"),
  plot_limits = c(-1.3, 1.3), 
  axis_text_size = 4,
  is_category = TRUE) +
  interior_annotation(label = "a3", cex = 2) + 
  scale_color_manual(values = c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854','#ffd92f','#e5c494'))

@@

trimesh_limb_best <- ggplot() + 
  geom_point(
    data = tsne_limb_scaled_with_cluster,
    aes(
      x = emb1,
      y = emb2,
      color = cluster
    ),
    alpha = 0.3
  ) +
  geom_segment(data = trimesh_data_limb, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#000000",
               linewidth = 1) +
  scale_color_manual(values = c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854','#ffd92f','#e5c494')) +
  interior_annotation("f1", cex = 2) +
  theme(
    aspect.ratio = 1
  )

@@

limb_proj_tsne_best_model1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2), # size, alpha, color
  plot_limits = c(-1.3, 1.4), 
  axis_text_size = 4,
  is_category = TRUE) +
  interior_annotation(label = "f2", cex = 2) + 
  scale_color_manual(values = c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854','#ffd92f','#e5c494'))

@@

limb_proj_tsne_best_model2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2), # size, alpha, color
  plot_limits = c(-1.3, 1.3), 
  axis_text_size = 4,
  is_category = TRUE) +
  interior_annotation(label = "f3", cex = 2) + 
  scale_color_manual(values = c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854','#ffd92f','#e5c494'))

>>>>

trimesh_limb <- ggplot() + 
  geom_point(
    data = tsne_limb_scaled_with_cluster,
    aes(
      x = emb1,
      y = emb2,
      color = cluster
    ),
    alpha = 0.3
  ) +
  geom_segment(data = trimesh_data_limb, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#000000",
               linewidth = 1) +
  scale_color_manual(values = c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854','#ffd92f','#a6cee3')) +
  interior_annotation("a1", cex = 2) +
  theme(
    aspect.ratio = 1
  )
```

@@

cluster_colors <- c(
    "0" = '#66c2a5', "1" = '#fc8d62', "2" = '#8da0cb',
    "3" = '#e78ac3', "4" = '#a6d854', "5" = '#ffd92f', "6" = '#a6cee3'
)

@@

# Add line segments
nldr_plt <- nldr_plt |>
    add_segments(
        data = trimesh_data_limb,
        x = ~x_from, y = ~y_from,
        xend = ~x_to, yend = ~y_to,
        line = list(color = "#000000", width = 0.5),
        inherit = FALSE,
        showlegend = FALSE,
        hoverinfo = "skip"  # <-- skip hover
    )

@@

langevitour_output <- langevitour::langevitour(point_data[1:num_highd_col],
                                               lineFrom = edge_data$from_reindexed,
                                               lineTo = edge_data$to_reindexed,
                                               group = factor(point_data$type,
                                                              c("0", "1", "2", "3", "4", "5", "6", "model")),
                                               pointSize = append(rep(point_sizes[1], NROW(df_b)),
                                                                  rep(point_sizes[2], NROW(df))),
                                               levelColors = c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854','#ffd92f','#a6cee3', "#000000"),
                                               link=shared_df,
                                               linkFilter=FALSE,
                                               width = "370px", height = "370px")

@@

limb_proj_tsne_model1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2), # size, alpha, color
  line_param = c(0.5, 0.3, "#000000"),
  plot_limits = c(-1.3, 1.4), 
  axis_text_size = 4,
  is_category = TRUE) +
  interior_annotation(label = "a2", cex = 2) + 
  scale_color_manual(values = c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854','#ffd92f','#a6cee3'))

@@

limb_proj_tsne_model2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2), # size, alpha, color
  line_param = c(0.5, 0.3, "#000000"),
  plot_limits = c(-1.3, 1.3), 
  axis_text_size = 4,
  is_category = TRUE) +
  interior_annotation(label = "a3", cex = 2) + 
  scale_color_manual(values = c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854','#ffd92f','#a6cee3'))

@@

trimesh_limb_best <- ggplot() + 
  geom_point(
    data = tsne_limb_scaled_with_cluster,
    aes(
      x = emb1,
      y = emb2,
      color = cluster
    ),
    alpha = 0.3
  ) +
  geom_segment(data = trimesh_data_limb, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#000000",
               linewidth = 1) +
  scale_color_manual(values = c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854','#ffd92f','#a6cee3')) +
  interior_annotation("f1", cex = 2) +
  theme(
    aspect.ratio = 1
  )

@@

limb_proj_tsne_best_model1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2), # size, alpha, color
  plot_limits = c(-1.3, 1.4), 
  axis_text_size = 4,
  is_category = TRUE) +
  interior_annotation(label = "f2", cex = 2) + 
  scale_color_manual(values = c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854','#ffd92f','#a6cee3'))

@@

limb_proj_tsne_best_model2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2), # size, alpha, color
  plot_limits = c(-1.3, 1.3), 
  axis_text_size = 4,
  is_category = TRUE) +
  interior_annotation(label = "f3", cex = 2) + 
  scale_color_manual(values = c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854','#ffd92f','#a6cee3'))
